Mealtime conversations between parents and their 2-year-old children in five cultural contexts

### 2022-12-06 manuscript/paper.Rmd
update paper for preprint

authornote: |
  This research was funded by a grant from Volkswagen Foundation (89611–2), awarded to P.K.. The data assessment in Kyoto was partly funded by a JSPS Fellowship to M.K.. We would like to thank all the research assistants who supported the data assessments and coding: Phileas Heim, Chisato Fukuda, Julia Ohlendorf, Marlene Abromeit. We are grateful to Luke Maurits for statistical advice.

@@

keywords          : "Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction"
wordcount         : "X"

@@

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

@@

classoption       : "man"
output            : papaja::apa6_pdf
---

@@

@@

@@

For each of the research questions (see below), we defined a response variable and then used Bayesian multilevel regression models fit via the function `brm` from the package `brms` [@burkner2017brms] to model the effect of cultural setting and -- whenever applicable -- that of the different individuals involved in the conversation. To make inferences about the importance of predictors, we compared a set of nested models including cultural setting and individual as predictors to each other and to a null model that did not include them to test if these predictors improved model fit. Following @mcelreath2018statistical, we compared models using Widely Applicable Information Criteria (WAIC) and the corresponding weights. This approach favors models that have high out-of-sample predictive accuracy in that they achieve a good fit to the data with the minimal set of parameters.

We modeled the effect of cultural settings as random effects and interactions between additional variables (e.g., speaker identity) and setting as random slopes within cultural setting (`brms` notation: `(variable|setting)`). This approach partially pools model estimates and is thought to yield more generalizable results because it avoids overfitting the model to the observed data [@gelman2006data; @mcelreath2018statistical]. For each model comparison, we visualized the predictions of the winning model and interpreted them based on their posterior means and 95% Credible Intervals (CrI). We used default priors built into `brms` for all parameters.

>>>>

authornote: |
  This research was funded by a grant from Volkswagen Foundation (89611–2), awarded to P.K.. The data assessment in Kyoto was partly funded by a JSPS Fellowship to M.K.. We would like to thank all the research assistants who supported the data assessments and coding: Phileas Heim, Chisato Fukuda, Julia Ohlendorf, Marlene Abromeit. We are grateful to Luke Maurits for statistical advice. All data and analysis code can be found in the following repository: https://github.com/ccp-eva/mealtime.

@@

keywords          : "Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction"
wordcount         : "7960"

@@

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : yes

@@

classoption       : "man"
output            : papaja::apa6_docx
---

@@

# Public significance statement

Cultural norms and beliefs structure social interactions and communication. As a consequence, children learn language under very different circumstances. We studied communicative interactions between parents and their children in five diverse cultural contexts. We found a common, child-centered pattern of communication that was attenuated in line with local norms and values. This suggests that children can rely on similar information sources and learning processes across cultural contexts.

# Introduction

@@

## Transparency and openness.

We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study. All data and analysis code can be found in the following repository: https://github.com/ccp-eva/mealtime. Data were analyzed using R, version 4.2.0 [@citeR] and the function `brm` from the package `brms` [@burkner2017brms]. We used default priors built into `brms` for all parameters. The study's design and its analysis were not pre-registered.

@@

For each of the research questions (see below), we defined a response variable and then used Bayesian multilevel regression models to model the effect of cultural setting and -- whenever applicable -- that of the different individuals involved in the conversation. To make inferences about the importance of predictors, we compared a set of nested models including cultural setting and individual as predictors to each other and to a null model that did not include them to test if these predictors improved model fit. Following @mcelreath2018statistical, we compared models using Widely Applicable Information Criteria (WAIC) and the corresponding weights. This approach favors models that have high out-of-sample predictive accuracy in that they achieve a good fit to the data with the minimal set of parameters.

We modeled the effect of cultural settings as random effects and interactions between additional variables (e.g., speaker identity) and setting as random slopes within cultural setting (`brms` notation: `(variable|setting)`). This approach partially pools model estimates and is thought to yield more generalizable results because it avoids overfitting the model to the observed data [@gelman2006data; @mcelreath2018statistical]. For each model comparison, we visualized the predictions of the winning model and interpreted them based on their posterior means and 95% Credible Intervals (CrI).

### 2022-12-06 manuscript/paper.tex
update paper for preprint

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction\newline\indent Word count: X}
\usepackage{lineno}

@@

This research was funded by a grant from Volkswagen Foundation (89611--2), awarded to P.K.. The data assessment in Kyoto was partly funded by a JSPS Fellowship to M.K.. We would like to thank all the research assistants who supported the data assessments and coding: Phileas Heim, Chisato Fukuda, Julia Ohlendorf, Marlene Abromeit. We are grateful to Luke Maurits for statistical advice.

@@

@@

@@

For each of the research questions (see below), we defined a response variable and then used Bayesian multilevel regression models fit via the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017) to model the effect of cultural setting and -- whenever applicable -- that of the different individuals involved in the conversation. To make inferences about the importance of predictors, we compared a set of nested models including cultural setting and individual as predictors to each other and to a null model that did not include them to test if these predictors improved model fit. Following McElreath (2018), we compared models using Widely Applicable Information Criteria (WAIC) and the corresponding weights. This approach favors models that have high out-of-sample predictive accuracy in that they achieve a good fit to the data with the minimal set of parameters.

We modeled the effect of cultural settings as random effects and interactions between additional variables (e.g., speaker identity) and setting as random slopes within cultural setting (\texttt{brms} notation: \texttt{(variable\textbar{}setting)}). This approach partially pools model estimates and is thought to yield more generalizable results because it avoids overfitting the model to the observed data (Gelman \& Hill, 2006; McElreath, 2018). For each model comparison, we visualized the predictions of the winning model and interpreted them based on their posterior means and 95\% Credible Intervals (CrI). We used default priors built into \texttt{brms} for all parameters.

@@

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Language acquisition, Communication, Gesture, Cross-cultural psychology, Parent-child interaction\newline\indent Word count: 7960}
\usepackage{lineno}

@@

This research was funded by a grant from Volkswagen Foundation (89611--2), awarded to P.K.. The data assessment in Kyoto was partly funded by a JSPS Fellowship to M.K.. We would like to thank all the research assistants who supported the data assessments and coding: Phileas Heim, Chisato Fukuda, Julia Ohlendorf, Marlene Abromeit. We are grateful to Luke Maurits for statistical advice. All data and analysis code can be found in the following repository: \url{https://github.com/ccp-eva/mealtime}.

@@

\hypertarget{public-significance-statement}{%
\section{Public significance statement}\label{public-significance-statement}}

Cultural norms and beliefs structure social interactions and communication. As a consequence, children learn language under very different circumstances. We studied communicative interactions between parents and their children in five diverse cultural contexts. We found a common, child-centered pattern of communication that was attenuated in line with local norms and values. This suggests that children can rely on similar information sources and learning processes across cultural contexts.

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{transparency-and-openness.}{%
\subsection{Transparency and openness.}\label{transparency-and-openness.}}

We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study. All data and analysis code can be found in the following repository: \url{https://github.com/ccp-eva/mealtime}. Data were analyzed using R, version 4.2.0 (R Core Team, 2022) and the function \texttt{brm} from the package \texttt{brms} (Bürkner, 2017). We used default priors built into \texttt{brms} for all parameters. The study's design and its analysis were not pre-registered.

@@

For each of the research questions (see below), we defined a response variable and then used Bayesian multilevel regression models to model the effect of cultural setting and -- whenever applicable -- that of the different individuals involved in the conversation. To make inferences about the importance of predictors, we compared a set of nested models including cultural setting and individual as predictors to each other and to a null model that did not include them to test if these predictors improved model fit. Following McElreath (2018), we compared models using Widely Applicable Information Criteria (WAIC) and the corresponding weights. This approach favors models that have high out-of-sample predictive accuracy in that they achieve a good fit to the data with the minimal set of parameters.

We modeled the effect of cultural settings as random effects and interactions between additional variables (e.g., speaker identity) and setting as random slopes within cultural setting (\texttt{brms} notation: \texttt{(variable\textbar{}setting)}). This approach partially pools model estimates and is thought to yield more generalizable results because it avoids overfitting the model to the observed data (Gelman \& Hill, 2006; McElreath, 2018). For each model comparison, we visualized the predictions of the winning model and interpreted them based on their posterior means and 95\% Credible Intervals (CrI).

@@

\leavevmode\vadjust pre{\hypertarget{ref-citeR}{}}%
R Core Team. (2022). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
